### 2019-07-11 manuscript/tables.tex
more tables

>>>>

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M2    & M3     & M4    & M5     & Evidence                                                                                     \\ \hline
M1. D/P              & -1283.76                                                          & 59.90 & 49.23  & 60.48 & 58.82  & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M1\end{tabular}            \\ \hline
\textbf{M2. CID D/P} & \textbf{-1223.86}                                                 &       & -10.66 & 0.579 & -1.079 & \begin{tabular}[c]{@{}l@{}}Moderate to strong \\ preference for M2\end{tabular}              \\ \hline
M3. D/P+A/B          & -1234.52                                                          &       &        & 11.24 & 9.58   & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
M4. D/P+A/B asym     & -1223.28                                                          &       &        &       & -1.658 & \begin{tabular}[c]{@{}l@{}}Moderate evidence for\\ only asymmetric hidden rates\end{tabular} \\\hline
M5. D/P+A/B all asym & -1224.93                                                          &       &        &       &        &          \\ \hline                                                                                   
\end{tabular}
\caption{Bayes factors of  ploidy only models without diplodization. Results indicate that a character independent model (M2) is strongly preferred over every other model. The following best model is M4 a HiSSE model with asymetric hidden rates.}
\label{table:M1M5}
\end{table}

\begin{table}
\addtolength{\tabcolsep}{-3pt}
\begin{tabular}{|l|r|c|c|c|c|l|}
\hline
Model                      & \begin{tabular}[c]{@{}l@{}}Marginal\\ log-likelihood\end{tabular} & M12   & M13   & M14   & M15   & Evidence                                                                                       \\ \hline
M11. I/C                   & -1309.07                                                          & 41.13 & 38.59 & 61.39 & 61.35 & \begin{tabular}[c]{@{}l@{}}Every model strongly \\ preferred over M111\end{tabular}            \\ \hline
M12. CID I/C               & -1267.93                                                          &       & -2.53 & 20.37 & 20.21 & \begin{tabular}[c]{@{}l@{}}Models with asymmetric rates\\ are preferred over  M12\end{tabular} \\ \hline
M13. I/C+A/B               & -1270.47                                                          &       &       & 22.80 & 22.75 & \begin{tabular}[c]{@{}l@{}}Asymmetric rates strongly\\ preferred over symmetric\end{tabular}   \\ \hline
\textbf{M14. I/C+A/B asym} & \textbf{-1247.66}                                                 &       &       &       & -0.05 & No evidence                                                                                    \\ \hline
M15. I/C+A/B all asym      & -1247.72                                                          &       &       &       &       &       \\ \hline                                                                                        
\end{tabular}
\caption{Bayes factors of breeding system only models. Results indicate that the HiSSE model with asymmetric hidden rates (M14) is strongly preferred over every other model very closely followed by M15 the model that adds asymmetry to the transition rates within hidden states.}
\label{table:M11M15}
\end{table}
